---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

# Business understanding
We will be using 4 variables to observe whether an office has been used or not. However, the table provides too much information - so, irrelevant information will be excluded.

# Data understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-Mendy1997/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
str(rawDF)
```

# Data preparation
The variable 'date' does not contain any important information, thus will be excluded. 

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

We will use this formula to see how many offices are occupied or not, (1: occupancy, 0: not occupied)

```{r}
cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
```
```{r}
propDiag
```

We will now change the "1" and "0" into "occupancy" and "not occupied"

```{r}
cleanDF$diagnosis <- factor(cleanDF$Occupancy, levels = c("1", "0"), labels = c("Occupancy", "Not occupied")) %>% relevel("Not occupied")
head(cleanDF, 10)
```
```{r}
summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2")])
```

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
```
```{r}
cat("testSet2:", testSet2, "\n")
```
```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
```
```{r}
cat("Normalized testSet2:", normalize(testSet2))
```
```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(2:nCols-1,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[c("Temperature", "Humidity", "Light", "CO2", "HumidityRatio")])
```

# Training the data

```{r}
trainDF_feat <- cleanDF_n[1:4000, 7]
testDF_feat <- cleanDF_n[4001:8143, 7]
```

# Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 57)
head(cleanDF_test_pred)
```

# Evaluation and Deployment

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = occupancy, dnn = c("Prediction", "True"))
```
reviewer adds suggestions for improving the model
